---
title: "comp20008assg2"
output: html_document
date: "2023-05-14"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(betareg)
library(lmtest)
```

```{r}
df = read.csv("~/jbdouz@gmail.com - Google Drive/My Drive/Colab Notebooks/comp20008assg2/cleaned_full_data.csv", row.names = "No..of.App.")
df_det = read.csv("~/jbdouz@gmail.com - Google Drive/My Drive/Colab Notebooks/comp20008assg2/cleaned_det_data.csv", row.names = "No..of.App.")
dim(df_det)[1]
```

# Model1: Beta regression to predict Adjudicate ratio
```{r}
# fixing missing values in amount of payment schedule
df_det$Amount.of.Payment.Schedule..ex.GST. = ifelse(is.na(df_det$Amount.of.Payment.Schedule..ex.GST.), 0, df_det$Amount.of.Payment.Schedule..ex.GST.)

# fixing extreme values in response
df_det$Adjudicate.ratio = ifelse(df_det$Adjudicate.ratio > 1, 1, df_det$Adjudicate.ratio)
df_det$Adjudicate.ratio.trans = (df_det$Adjudicate.ratio * (dim(df_det)[1] - 1) + 0.5) / dim(df_det)[1]
```

```{r}
beta.f.main = betareg(Adjudicate.ratio.trans ~ Claimed.amount..ex.GST. + Amount.of.Payment.Schedule..ex.GST. + factor(Region.name) + factor(Work.category) + factor(Section.of.Act.application.made.under) + factor(Business.Type.Activity..Claimant.) + factor(Business.Structure..Claimant.) + factor(Claimant.advisers) + factor(Business.Type.Activity..Respondent.) + factor(Business.Structure..Respondent.) + factor(Respondent.advisers) + factor(s21.2B..new.reasons.provided.by.Respondent) + factor(s22.4..b..extension.of.time.sought), data = df_det, link="logit")
summary(beta.f.main, type="deviance")
```
```{r}
beta1.main = betareg(Adjudicate.ratio.trans ~ factor(Work.category) + factor(Section.of.Act.application.made.under) + factor(Claimant.advisers) + factor(Business.Type.Activity..Respondent.), data = df_det, link="logit")
summary(beta1.main, type="deviance")
```

```{r}
beta2.main = betareg(Adjudicate.ratio.trans ~ factor(Section.of.Act.application.made.under) + factor(Claimant.advisers) + factor(Business.Type.Activity..Respondent.), data = df_det, link="logit")

beta3.main = betareg(Adjudicate.ratio.trans ~ factor(Section.of.Act.application.made.under) + factor(Claimant.advisers), data = df_det, link="logit")
```


```{r}
lrtest(beta.f.main, beta1.main, beta2.main, beta3.main)

summary(beta2.main)
```

## Try interaction terms between categorical variables
pairwise zero structure problem, very hard to tackle
```{r}
# beta.f.inter = betareg(Adjudicate.ratio.trans ~ Claimed.amount..ex.GST. + Amount.of.Payment.Schedule..ex.GST. + (factor(Region.name) + factor(Work.category) + factor(Section.of.Act.application.made.under) + factor(Business.Type.Activity..Claimant.) + factor(Business.Structure..Claimant.) + factor(Claimant.advisers) + factor(Business.Type.Activity..Respondent.) + factor(Business.Structure..Respondent.) + factor(Respondent.advisers) + factor(s21.2B..new.reasons.provided.by.Respondent) + factor(s22.4..b..extension.of.time.sought))^2, data = df_det, link="logit")
```


```{r}
beta.f.main.loglog = betareg(Adjudicate.ratio.trans ~ Claimed.amount..ex.GST. + Amount.of.Payment.Schedule..ex.GST. + factor(Region.name) + factor(Work.category) + factor(Section.of.Act.application.made.under) + factor(Business.Type.Activity..Claimant.) + factor(Business.Structure..Claimant.) + factor(Claimant.advisers) + factor(Business.Type.Activity..Respondent.) + factor(Business.Structure..Respondent.) + factor(Respondent.advisers) + factor(s21.2B..new.reasons.provided.by.Respondent) + factor(s22.4..b..extension.of.time.sought), data = df_det, link="loglog")
summary(beta.f.main.loglog, type="deviance")
```

```{r}
beta1.main.loglog = betareg(Adjudicate.ratio.trans ~ factor(Work.category) + factor(Section.of.Act.application.made.under) + factor(Claimant.advisers) + factor(Business.Type.Activity..Respondent.), data = df_det, link="loglog", subset = !(row.names(df_det) %in% c("32", "69", "97", "109", "151", "56", "111", "113", "208", "222", "124")))

beta1.main.loglog = betareg(Adjudicate.ratio.trans ~ factor(Work.category) + factor(Section.of.Act.application.made.under) + factor(Claimant.advisers) + factor(Business.Type.Activity..Respondent.), data = df_det, link="loglog")

beta2.main.loglog = betareg(Adjudicate.ratio.trans ~ factor(Section.of.Act.application.made.under) + factor(Claimant.advisers), data = df_det, link="loglog", subset = !(row.names(df_det) %in% c("32", "69", "97", "109", "151", "56", "111", "113", "208", "222", "124")))

lrtest(beta1.main.loglog, beta2.main.loglog)

summary(beta2.main.loglog)
```


```{r}
AIC(beta2.main, beta2.main.loglog)
```

```{r}
# fitting logistic regression model
logistic.f.main = glm(Adjudicate.ratio.binary ~ Claimed.amount..ex.GST. + Amount.of.Payment.Schedule..ex.GST. + factor(Region.name) + factor(Work.category) + factor(Section.of.Act.application.made.under) + factor(Business.Type.Activity..Claimant.) + factor(Business.Structure..Claimant.) + factor(Claimant.advisers) + factor(Business.Type.Activity..Respondent.) + factor(Business.Structure..Respondent.) + factor(Respondent.advisers) + factor(s21.2B..new.reasons.provided.by.Respondent) + factor(s22.4..b..extension.of.time.sought), data = df_det, family="binomial")
summary(logistic.f.main)
```
```{r}
logistic1.main = step(logistic.f.main, trace = FALSE)
logistic1.main = glm(formula = factor(Adjudicate.ratio.binary) ~ factor(Work.category) + 
    factor(Section.of.Act.application.made.under) + factor(Claimant.advisers) + 
    factor(Business.Type.Activity..Respondent.) + factor(Business.Structure..Respondent.), 
    family = "binomial", data = df_det, subset = !(row.names(df_det) %in% c("32", "69", "97", "109", "151", "56", "111", "113", "208", "222", "124")))
logistic2.main = step(logistic1.main, trace = FALSE)

logistic3.main = glm(formula = factor(Adjudicate.ratio.binary) ~  
    factor(Section.of.Act.application.made.under) + factor(Claimant.advisers) + 
    factor(Business.Structure..Respondent.), family = "binomial", 
    data = df_det, subset = !(row.names(df_det) %in% c("32", 
        "69", "97", "109", "151", "56", "111", "113", "208", 
        "222", "124")))

anova(logistic1.main, logistic2.main, logistic3.main, test = "Chi")

summary(logistic2.main)
```
## structural zero issues: 
work category only has 1 case and it's 0, no 32
'Section of Act application made under' == "s.18(1)(a)(ii)" only has 3 cases and all are 1, no 69, 97, 109
'Claimant advisers' == "Consultant", no 151
'Business Type/Activity (Respondent)' == "Major Subcontractor", no 56
'Business Type/Activity (Respondent)' == "Other", no 111, 113, 208, 222
'Business Type/Activity (Respondent)' == "Project manager", no 124


# Model 2: Reverse engineering how Government calculate Certificate fee

# Model 3: 




